Davos: a Python package ``smuggler'' for constructing lightweight reproducible notebooks

### 2023-09-18 paper/main.tex
add reference to config section

By default, each Davos-enhanced notebook will create and use its own notebook-specific project named for the absolute path to the notebook file. 
However, before smuggling its required packages, a notebook may be set to instead use an arbitrarily named, notebook-agnostic project by assigning any string (that is a valid Unix directory name) to \texttt{davos.project}.
This provides a convenient way for multiple related notebooks that share a common set of requirements to use the same Davos project, by setting \texttt{davos.project} to the same string in each one. 
%This provides a convenient way to share a single Davos project across multiple related notebooks that share a common set of requirements, by setting \texttt{davos.project} to the same string in each one. 
It is also possible (though not recommended) to disable Davos's project system entirely and install smuggled packages directly into the user's Python environment by setting \texttt{davos.project} to \texttt{None}.

>>>>

By default, each Davos-enhanced notebook will create and use its own notebook-specific project named for the absolute path to the notebook file.
However, before smuggling its required packages, a notebook may be set to instead use an arbitrarily named, notebook-agnostic project by assigning any string (that is a valid Unix directory name) to \texttt{davos.project} (see Sec.~\ref{subsec:config}).
This provides a convenient way for multiple related notebooks that share a common set of requirements to use the same Davos project, by setting \texttt{davos.project} to the same string in each one.
%This provides a convenient way to share a single Davos project across multiple related notebooks that share a common set of requirements, by setting \texttt{davos.project} to the same string in each one.
It is also possible (though not recommended) to disable Davos's project system entirely and install smuggled packages directly into the user's Python environment by setting \texttt{davos.project} to \texttt{None}.
